\documentclass[11pt, english]{article}
        \usepackage{geometry}
                \geometry{
                        a4paper,total={210mm,297mm},
                        tmargin=40mm,
                        bmargin=40mm,
                        lmargin=48mm,
                        rmargin=48mm,
                }

        \usepackage{titlesec}

                \titleformat{\section}
                        {\fontsize{22}{16}\fmmfamily}{}{0em}{}
                \titleformat{\subsection}
                        {\fontsize{18}{16}\centering\fmmfamily}{}{0em}{}

	\newcommand{\HRule}[1]{\rule{\linewidth}{#1}}
                \setcounter{tocdepth}{5}
                \setcounter{secnumdepth}{5}

        \usepackage[T1]{fontenc}
        \usepackage{miama}
        %\usepackage{calligra}
        %\usepackage{CormorantGaramond}

        %\usepackage[utf8]{inputenc}
        %\usepackage{bickham}
        %\usepackage{calligra}
        %\usepackage{dutchcal}

	\usepackage{hyperref}
                \hypersetup{
                        colorlinks=true,
                        linkcolor=black,
                        filecolor=magenta,
                        urlcolor=cyan,
                        }

	\setlength{\parindent}{0pt}
        \usepackage{setspace}

\begin{document}

\pagenumbering{gobble}

	\title{
		\HRule{0.5pt}\\ [-0.7cm]
		\HRule{0.5pt}\\ [-0.125cm]
		\Huge\fmmfamily{Virtuous Truffle Company}\\
		\Large\fmmfamily{Premium Confectionery}
		\HRule{0.5pt}\\ [-0.7cm]
		\HRule{0.5pt}\\ [-1.5cm]
		}
        \author{\textit{}}
        \date{}
        \maketitle

\begin{center}
	\scriptsize
\begin{tabular}{r|l}
	\textsc{Mail To:} vtc.truffles@yahoo.com & \textsc{Telephone:} 07415 212 056\\
	\textsc{Website:} \href{http://vtctruffles.co.uk}{vtctruffles.co.uk} & \textsc{Address:} 0/1, 94 Braidholm Rd. G46 6DF\\
\end{tabular}
\end{center}

\section{A Scottish Confectionery Business}

\footnotesize Virtuous Truffle Company was formed in 2019 by two university students, but run for the majority of the time by one, now, soon-to-be graduate. We loved seeing the ever-growing local businesses around East Renfrewshire in 2019 and desperately wanted to be a part of the trend. 2019--2020 saw us lucky enough reach much desired success in direct sales, customer loyalty and excellent reception of products. It's now that we wish to take the next step and integrate ourselves in the atmosphere and warm relationships of the amazing businesses and establishments we have around us.\\

Yes, the name is a meme. However, the meaning is true. Of course to some degree, this business is `virtuous'; our most valued requirements come from \textit{quality}, \textit{awareness} and \textit{environment}. That's, an extremely high quality product, ingredients and service; full awareness about how products are made and from where ingredients are sourced; and, minimal unecessary negative impact on environmental issues. Not in a soy way but, in a way which allows us to provide the most sensible and sustainable products and packaging, at the best price.

\section{Our Offer}

\footnotesize We would love to be a part of your business and culture. Whether that's one of our \textit{Himalayan Salted Caramel} truffles served alongside a cortado at the end of a meal, a thrilling \textit{Coconut Lime \& Pistachio} truffle as a countertop treat to catch the eyes of your gazing customers, or a pyramid of our \textit{Grapefruit Gin} truffles served to those who like to live life on the edge. We would love to work with you to become a greater part of the community.\\

The decision is yours. Please see our \href{http://vtctruffles.co.uk/Truffles.html}{collection of truffles} and \textbf{choose one box} to sample for \textbf{free}. Just \textbf{email} me (Lewis Britton) with the name of your establishment and the product you wish to try, and they'll be delivered ASAP. When you fall in love with them, just get in touch and let's do something! If not, hey ho, you have a free box of the best truffles in East Renfrewshire.\\

Your consideration is much appreciated.\\

Sincerely yours,\\
Lewis Britton

\end{document}
